---
title: "MUSA8010ModelBuild"
author: "Trevor Kapuvari"
date: "2024-01-30"
output:
  html_document:
    toc: yes
    theme: cosmo
    toc_float: yes
    code_folding: hide
    number_sections: yes
---
# Introduction

# Exploratary Analysis
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat)
library(raster)
library(spdep)
library(FNN)
library(grid)
library(gridExtra)
library(knitr)
library(kableExtra)
library(tidycensus)
library(classInt)
library(RCurl)
library(httr)
```

```{r load data}
path <- 'https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/tree/main/Data/'

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

litter_id <- '1xtwbhs6bHGufxMK6-BjZO7mPECRmIzeW'
litter <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", id))

litter_p <- litter%>%
  filter(master_material == 'PLASTIC')%>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant")%>%
  st_transform('ESRI:102271')

chen_bdry <- st_read('https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/gcc-divisions-latest.kml?token=GHSAT0AAAAAACM4UMDDOD2UHU5S3ZWOZP66ZOBMFRQ')
chen_bdry <- st_set_crs(chen_bdry, 4326)%>%
  st_transform('ESRI:102271')

chen_zone <- st_read('https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/gcc-zones-latest.kml?token=GHSAT0AAAAAACM4UMDDRP6PRGP7J6VXKBZUZOBKQ2Q')%>%
  st_transform('ESRI:102271')
```

## statistical analysis of litter dataset
what's about the litter dataset?
  1. master_item_name histogram
  2. quantity histogram
  3. altitude
  4. radius 
  5. location distribution
```{r}
grid.arrange(
  ggplot(litter_p, aes(x = quantity)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Count of Quantity Per Record",
       x = "Category",
       y = "Count"),
  ggplot(litter_p, aes(x = altitude)) + 
  geom_histogram() +
  theme_minimal() +
  labs(title = "Altitude Histogram",
       x = "Category",
       y = "Count"),
  ggplot(litter_p, aes(x = radius)) + 
  geom_histogram() +
  theme_minimal() +
  labs(title = "Radius Histogram",
       x = "Category",
       y = "Count"),
  ncol = 3
)
```

```{r}
ggplot(litter_p, aes(x = master_item_name)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Count of Main Item Category",
       x = "Category",
       y = "Count")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
ggplot(litter_p, aes(x = location)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Count of Location in Litter Record",
       x = "Category",
       y = "Count")+
  theme(axis.text.x = element_text(angle = 25,size = 6))
```

## what about potential relevant social-econmic variables?
  1. slum
  2. population (density)
  3. 
```{r}
chen_bdry <- st_read("https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/gcc-divisions-latest.kml?token=GHSAT0AAAAAACM4UMDCNXPWYGVQ6LZESKBEZOBKQMA")
chen_bdry <- st_set_crs(chen_bdry, 4326)%>%
  st_transform('ESRI:102271')

chen_zone <- st_read('https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/gcc-zones-latest.kml?token=GHSAT0AAAAAACM4UMDDRP6PRGP7J6VXKBZUZOBKQ2Q')

chen_slum <- st_read('https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/chennai_slums.kml?token=GHSAT0AAAAAACM4UMDDSLLVAMRRTCPGZTPEZOBKMUA')%>%
  st_transform('ESRI:102271')

chen_slum_bdry <- st_read("https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/chennai_slum_boundaries.kml?token=GHSAT0AAAAAACM4UMDCLCNN6TCNVCPK5YCWZOBKNMQ")

chen_pop <- read.csv('https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/Chennai_pop_2020estimation.csv?token=GHSAT0AAAAAACM4UMDDAX3NFCPJGHH6GNXYZOBKOPA')
```

```{r}
fishnet <- 
  st_make_grid(chen_bdry,
               cellsize = 500, 
               square = TRUE) %>%
  .[chen_bdry] %>%            
  st_sf() %>%
  mutate(uniqueID = 1:n())

slum_net <- 
  dplyr::select(chen_slum) %>% 
  mutate(countslum = 1) %>% 
  aggregate(., fishnet, sum) %>%
  mutate(countslum = replace_na(countslum, 0),
         uniqueID = 1:n(),
         cvID = sample(round(nrow(fishnet) / 24), 
                       size=nrow(fishnet), replace = TRUE))

grid.arrange(
  ggplot() +
  geom_sf(data = slum_net, aes(fill = countslum), color = NA) +
  scale_fill_viridis() +
  labs(title = "Slum count for the fishnet") +
  mapTheme(),
  ggplot() + 
  geom_sf(data = chen_bdry) +
  geom_sf(data = chen_slum, colour="red", size=0.2, show.legend = "point") +
  labs(title= "Slum, Chennai") +
  mapTheme(title_size = 14),
  nrow = 1
)
```

```{r}
chen_pop_sp <- merge(chen_bdry, chen_pop, by.x = 'Name', by.y = 'Div', all.x = TRUE)

grid.arrange(
  ggplot() +
  geom_sf(data = chen_pop_sp, aes(fill = PopulationEsti2020), color = NA) +
  scale_fill_viridis() +
  labs(title = "Popultion in Chennai") +
  mapTheme(),
  ggplot() +
  geom_sf(data = chen_pop_sp, aes(fill = PopulationDensity), color = NA) +
  scale_fill_viridis() +
  labs(title = "Pop Density in Chennai") +
  mapTheme(),nrow = 1
)
```

## what's about geospatial things?
  1. point map
  2. density map (general distribution trend illustration)
  3. fishnet map (analysis into unit)
  4. KNN map (one way to make assumption of the spatal distribution?)
  5. Local Moran's I analysis

```{r}
grid.arrange(
  ggplot() + 
  geom_sf(data = chen_bdry) +
  geom_sf(data = litter_p, colour="red", size=0.2, show.legend = "point") +
  labs(title= "Litter, Chennai") +
  mapTheme(title_size = 14),
  ggplot() + 
  geom_sf(data = chen_bdry, fill = "grey40") +
  stat_density2d(data = data.frame(st_coordinates(litter_p)), 
                 aes(X, Y, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 80, geom = 'polygon') +
  scale_fill_viridis() +
  scale_alpha(range = c(0.00, 0.35), guide = FALSE) +
  labs(title = "Density of Litter, Chennai") +
  mapTheme(title_size = 14) + theme(legend.position = "none"),
  nrow=1
)
```

```{r}
fishnet <- 
  st_make_grid(chen_bdry,
               cellsize = 500, 
               square = TRUE) %>%
  .[chen_bdry] %>%            
  st_sf() %>%
  mutate(uniqueID = 1:n())

litter_net <- 
  dplyr::select(litter_p) %>% 
  mutate(countlitter = 1) %>% 
  aggregate(., fishnet, sum) %>%
  mutate(countlitter = replace_na(countlitter, 0),
         uniqueID = 1:n(),
         cvID = sample(round(nrow(fishnet) / 24), 
                       size=nrow(fishnet), replace = TRUE))

ggplot() +
  geom_sf(data = litter_net, aes(fill = countlitter), color = NA) +
  scale_fill_viridis() +
  labs(title = "Count of Litter for the fishnet") +
  mapTheme()
```

```{r}
l_p <- litter_p%>%
  dplyr::select(list_name,geometry)
vars_net <- l_p%>%
  st_join(fishnet, join=st_within) %>%
  st_drop_geometry() %>%
  group_by(uniqueID,list_name) %>%
  summarize(count = n()) %>%
  left_join(fishnet, ., by = "uniqueID") %>%
  spread(list_name, count, fill=0) %>%
  dplyr::select(-`<NA>`) %>%
  ungroup()
```

```{r}
# convinience to reduce length of function names.
st_c    <- st_coordinates
st_coid <- st_centroid

## create NN from abandoned cars
vars_net <- vars_net %>%
    mutate(litter.nn = nn_function(st_c(st_coid(vars_net)), 
                                           st_c(l_p),
                                           k = 3))
```

```{r}
## Visualize the NN feature
vars_net.long.nn <- 
  dplyr::select(vars_net, ends_with(".nn")) %>%
    gather(Variable, value, -geometry)

ggplot() +
      geom_sf(data = vars_net.long.nn, aes(fill=value), colour=NA) +
      scale_fill_viridis(name="NN Distance") +
      labs(title="Litter NN Distance") +
      mapTheme()
```


  