---
title: "MUSA8010ModelBuild"
author: "Trevor Kapuvari"
date: "2024-01-30"
output: html_document
---
# Introduction

# Exploratary Analysis
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat)
library(raster)
library(spdep)
library(FNN)
library(grid)
library(gridExtra)
library(knitr)
library(kableExtra)
library(tidycensus)
library(classInt)
library(RCurl)
```

```{r load data}
path <- 'https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/tree/main/Data/'

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

litter <- read.csv('https://raw.githubusercontent.com/TrevorKap/MUSA810-Marine-Pollution/main/Data/mdt-dataChennai.csv?token=GHSAT0AAAAAACM4UMDCEPEVW3ZZLNQQVHLYZOAQ4CA')

litter_p <- litter%>%
  filter(master_material == 'PLASTIC')%>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326, agr = "constant")%>%
  st_transform('ESRI:102271')

chen_bdry <- st_read("/Users/mr.smile/Desktop/UPENN/Spring24/CPLN790/data/gcc-zones-latest.kml")
chen_bdry <- st_set_crs(chen_bdry, 4326)%>%
  st_transform('ESRI:102271')

chen_zone <- st_read('/Users/mr.smile/Desktop/UPENN/Spring24/CPLN790/data/gcc-divisions-latest.kml')%>%
  st_transform('ESRI:102271')
```

## statistical analysis of litter dataset
what's about the litter dataset?
  1. master_item_name histogram
  2. quantity histogram
  3. altitude
  4. radius 
  5. location distribution
```{r}
grid.arrange(
  ggplot(litter_p, aes(x = quantity)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Count of Quantity Per Record",
       x = "Category",
       y = "Count"),
  ggplot(litter_p, aes(x = altitude)) + 
  geom_histogram() +
  theme_minimal() +
  labs(title = "Altitude Histogram",
       x = "Category",
       y = "Count"),
  ggplot(litter_p, aes(x = radius)) + 
  geom_histogram() +
  theme_minimal() +
  labs(title = "Radius Histogram",
       x = "Category",
       y = "Count"),
  ncol = 3
)
```

```{r}
ggplot(litter_p, aes(x = master_item_name)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Count of Main Item Category",
       x = "Category",
       y = "Count")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
ggplot(litter_p, aes(x = location)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Count of Location in Litter Record",
       x = "Category",
       y = "Count")+
  theme(axis.text.x = element_text(angle = 25,size = 6))
```

what's about geospatial things?
  1. point map
  2. density map (general distribution trend illustration)
  3. fishnet map (analysis into unit)
  4. KNN map (one way to make assumption of the spatal distribution?)
  5. Local Moran's I analysis

```{r}
grid.arrange(
  ggplot() + 
  geom_sf(data = chen_bdry) +
  geom_sf(data = litter_p, colour="red", size=0.2, show.legend = "point") +
  labs(title= "Litter, Chennai") +
  mapTheme(title_size = 14),
  ggplot() + 
  geom_sf(data = chen_bdry, fill = "grey40") +
  stat_density2d(data = data.frame(st_coordinates(litter_p)), 
                 aes(X, Y, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 80, geom = 'polygon') +
  scale_fill_viridis() +
  scale_alpha(range = c(0.00, 0.35), guide = FALSE) +
  labs(title = "Density of Litter, Chennai") +
  mapTheme(title_size = 14) + theme(legend.position = "none"),
  nrow=1
)
```

```{r}
fishnet <- 
  st_make_grid(chen_bdry,
               cellsize = 500, 
               square = TRUE) %>%
  .[chen_bdry] %>%            # fast way to select intersecting polygons
  st_sf() %>%
  mutate(uniqueID = 1:n())

litter_net <- 
  dplyr::select(litter_p) %>% 
  mutate(countlitter = 1) %>% 
  aggregate(., fishnet, sum) %>%
  mutate(countlitter = replace_na(countlitter, 0),
         uniqueID = 1:n(),
         cvID = sample(round(nrow(fishnet) / 24), 
                       size=nrow(fishnet), replace = TRUE))

ggplot() +
  geom_sf(data = litter_net, aes(fill = countlitter), color = NA) +
  scale_fill_viridis() +
  labs(title = "Count of Litter for the fishnet") +
  mapTheme()
```

```{r}
l_p <- litter_p%>%
  dplyr::select(list_name,geometry)
vars_net <- l_p%>%
  st_join(fishnet, join=st_within) %>%
  st_drop_geometry() %>%
  group_by(uniqueID,list_name) %>%
  summarize(count = n()) %>%
  left_join(fishnet, ., by = "uniqueID") %>%
  spread(list_name, count, fill=0) %>%
  dplyr::select(-`<NA>`) %>%
  ungroup()
```

```{r}
# convinience to reduce length of function names.
st_c    <- st_coordinates
st_coid <- st_centroid

## create NN from abandoned cars
vars_net <- vars_net %>%
    mutate(litter.nn = nn_function(st_c(st_coid(vars_net)), 
                                           st_c(l_p),
                                           k = 3))
```

```{r}
## Visualize the NN feature
vars_net.long.nn <- 
  dplyr::select(vars_net, ends_with(".nn")) %>%
    gather(Variable, value, -geometry)

ggplot() +
      geom_sf(data = vars_net.long.nn, aes(fill=value), colour=NA) +
      scale_fill_viridis(name="NN Distance") +
      labs(title="Litter NN Distance") +
      mapTheme()
```
  
  